Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Remove redundant text from "Introduction"

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.  Hspec inspired by
RSpec~\cite{rspec} allows to document code with \emph{properties} and
\emph{code examples}, and create an informal specification document
from that.

@@

For this purpose, we brought a test method from other programming
language community and extended missing features.  In particular, we
introduced Doctest~\cite{doctest} and integrated it with
QuickCheck~\cite{quickcheck} for user documentation.

\begin{itemize}
    \item
        We proposed some combinators to set expectations about
        \emph{code examples}.
\end{itemize}

Automating such as test discovery and continuous integration (CI) ~\cite{ci}
is an important aspect of BDD.
We improve CI suport for Doctest and Hspec.

@@

\begin{itemize}
\item
    Implement Doctest in Haskell and add support for QuickCheck properties to Doctest (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

>>>>

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.  Hspec, inspired by
RSpec~\cite{rspec}, allows to document Haskell code with
\emph{properties} and \emph{code examples}, verifies examples and
tests properties, and creates an informal specification document.

@@

Automation, such as test discovery and continuous integration (CI)
~\cite{ci} is an important aspect of BDD.

@@

\begin{itemize}
\item
    Add support for QuickCheck properties to Doctest (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})
